Total Score

### 2023-01-31 src/MSAtotal_scores.Rmd
added owen's emailed weight calculations Jan 31.

>>>>

```{r climate risk 35 and Jan 31 weights from owen}

weights_climate35_owen <- c(0.25, 0.1, 0.15, 0.075, 0.0, 0.075, 0.35)

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate35_owen = cbsa)#this is just a place holder

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$score_climate35_owen[i] = weighted.mean(cbsa_data, weights_climate35_owen) 
}
```
